---
title: "Day 1 mini-project"
author: "Louis Raison & Pierre-Henri Ramirez"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r}

# INSTRUCTIONS

# You are a seasoned data scientist who has just arrived in Boston. You're looking to go see the sights, but you don't know where they are! Instead of buying a tourist guide like a Muggle, you are going to use your skills in exploratory data analysis and visualization to identify some of the cool spots to visit. 

# Working with your partner, conduct analyses to identify at least THREE cool spots that you want to check out. Use the dashboard format to communicate your findings. You can check e.g. on Google to confirm your findings, but you should include clear commentary indicating how your analysis supports your findings. I've included some of the code from the script we worked on together to help you get started. 

```

```{r}
# You may find the following resources useful: 
# - Your team member(s)! 
# - Data wrangling [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf), 
# - `R` graphics [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf), 
# - [`R` Graphics Cookbook](http://www.cookbook-r.com/Graphs/)
# - [RMarkdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
```

```{r data_prep}
# put your data preparation code here. To get you started, the data preparation we performed in the session previously has already been pasted in. Feel free to add any additional data preparation code needed for your visualizations

listings <- read_csv('../../data/listings.csv')
calendar <- read_csv('../../data/calendar.csv')

source("clean_prices.R")
listings <- clean_prices(listings)
calendar <- clean_prices(calendar)
```

# Average Disponibility per neighbourhood

```{r box_1}

listings %>%
  left_join(calendar,
            by = c('id' = 'listing_id'))%>%
  group_by(neighbourhood) %>%
  summarise(availability_avg = mean(available)) %>%
  arrange((availability_avg))%>%
  head(5)


```


One indicator which we thought of is the average availability. Indeed, the locations in the most wanted neighbourhoods will be more demanded than the others. Making the inverse of the availability a good indicator of neighbourhoods' attractiveness. Find Above the top five neighbourhoods in terms of that indicator.

# Price Variation Over Time


Column {data-width=500}
-----------------------------------------------------------------------

### Average variation of the prices in Boston

```{r box_4}
calendar %>%
    group_by(date) %>%
    summarise(avg_price = mean(price)) %>%
    ggplot() +
    aes(x = date, y= avg_price) +
    geom_line() +
    theme_bw()
```

### Prices around April

```{r box_5}
calendar %>%
    group_by(date) %>%
    filter(month(date)==4, day(date)>15, day(date)<25)%>%
    summarise(avg_price = mean(price))
```

### 

The evolution of the price around Boston is really straightforward, as there is a normal rise of the average price in the summer. However, there is a weird pike around the end of April, that wecan identify more precisely by selecting the right period of time, from April 17th to April 20th.

There seems to be somthing really interesting happening there, and we might be able to learn more about the location by checking the neighbourhoods where the rise is the steepest.


Column {data-width=500}
-----------------------------------------------------------------------

### Variation of the prices around April

We can see that the prices within the different neighbourhoods vary very differently around that time.

By selecting only Mission Hill, we can see that this neighbourhood is probably very interesting to go around that time. Actually, this spot is on the course of the Boston 2020 marathon, which might be an explanation for it. (see next tab)

### Variation of the different neighbourhood prices

```{r box_7}
# Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 

# This is not a good visualization -- always remember to include titles and legends. Make yours better! 

neighbourhood_lookup <- listings %>% 
	select(id, neighbourhood)

calendar %>% 
	left_join(neighbourhood_lookup, by = c('listing_id' = 'id')) %>% 
	group_by(neighbourhood, date) %>% 
	summarise(price = mean(price), n = n()) %>% 
	filter(n > 100) %>%
	ggplot() +
	aes(x = date, y = price, color = neighbourhood) + 
	geom_line()+
    guides(color = FALSE)+
    theme(aspect.ratio=0.5)
```

# Mission Hill Overview

```{r box_6}
# Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 

# This is not a good visualization -- always remember to include titles and legends. Make yours better! 

neighbourhood_lookup <- listings %>% 
	select(id, neighbourhood)

calendar %>% 
	left_join(neighbourhood_lookup, by = c('listing_id' = 'id')) %>% 
    filter(neighbourhood == "Mission Hill") %>%
	group_by(neighbourhood, date) %>% 
	summarise(price = mean(price), n = n()) %>% 
	filter(n > 100) %>%
	ggplot() +
	aes(x = date, y = price, color = neighbourhood) + 
	geom_line()+
    theme(aspect.ratio=0.5)
```

# Users location reviews

```{r box}

listings %>%
  left_join(calendar,
            by = c('id' = 'listing_id'))%>%
  group_by(neighbourhood) %>%
  summarise(avg_scores_location = mean(review_scores_location, na.rm = T), number_locations=n()) %>%
  arrange((desc(avg_scores_location)), desc(number_locations))%>%
  head(5)

```

Above, we would recommend Financial District and the Government Center. According to the average score location given by the renters. As there are many equal to 10, the maximum, we discriminate by the number of locations, which describes the weigh of the meaning of these scores. 
